mass map reconstruction with sparsity method

### 2019-10-20 ms_method_HSCY1/ms.tex

\begin{document}
\title{FPFS Shear Estimator: Systematic Tests on the First Year Hyper Suprime-Cam Survey}
\author{Xiangchong Li}
\affiliation{Department of Physics, University of Tokyo, Tokyo 113-0033, Japan}
\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
University of Tokyo, Kashiwa 277-8583, Japan}
\author{Masamune Oguri}
\affiliation{Department of Physics, University of Tokyo, Tokyo 113-0033, Japan}
\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
University of Tokyo, Kashiwa 277-8583, Japan}
\affiliation{Research Center for the Early Universe, University of Tokyo, Tokyo 113-0033, Japan}
\author{Nobuhiko Katayama}
\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
University of Tokyo, Kashiwa 277-8583, Japan}
\author{Wentao Luo}
\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
University of Tokyo, Kashiwa 277-8583, Japan}
\author{Wenting Wang}
\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
University of Tokyo, Kashiwa 277-8583, Japan}
\author{Jiaxin Han}
\affiliation{Department of Astronomy, School of Physics and Astronomy, Shanghai Jiao Tong University, Shanghai, 200240, China}
\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
University of Tokyo, Kashiwa 277-8583, Japan}
\author{HSC Collaboration}
\noaffiliation
\email{xiangchong.li@ipmu.jp}

%\author{Surhud More}
%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (Kavli IPMU, WPI),\\
%UTIAS, Tokyo Institutes for Advanced Study, University of Tokyo, Chiba 277-8583, Japan}

@@

\section{Mass Map}
\label{sec:kappaMap}

>>>>

\begin{document}
\title{mass map reconstruction with sparsity method}
%\author{Xiangchong Li}
%\affiliation{Department of Physics, University of Tokyo, Tokyo 113-0033, Japan}
%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
%University of Tokyo, Kashiwa 277-8583, Japan}
%\author{Masamune Oguri}
%\affiliation{Department of Physics, University of Tokyo, Tokyo 113-0033, Japan}
%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
%University of Tokyo, Kashiwa 277-8583, Japan}
%\affiliation{Research Center for the Early Universe, University of Tokyo, Tokyo 113-0033, Japan}
%\author{Nobuhiko Katayama}
%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
%University of Tokyo, Kashiwa 277-8583, Japan}
%\author{Wentao Luo}
%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
%University of Tokyo, Kashiwa 277-8583, Japan}
%\author{Wenting Wang}
%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
%University of Tokyo, Kashiwa 277-8583, Japan}
%\author{Jiaxin Han}
%\affiliation{Department of Astronomy, School of Physics and Astronomy, Shanghai Jiao Tong University, Shanghai, 200240, China}
%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe (WPI),\\
%University of Tokyo, Kashiwa 277-8583, Japan}
%\author{HSC Collaboration}
%\noaffiliation
%\email{xiangchong.li@ipmu.jp}

@@

\section{The Method}
\label{sec:kappaMap}
